Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-05-16 manuscript.tex
reccurrence plot and legend

Figure \ref{fig_occurrence} presents the catalog \gls{mfd}.
A general $b=1$ fit is also plotted, and the completeness magnitude on the incremental distribution is about 3.0.

@@

%------------------------------------------------
%
% smooothing methods
%
%------------------------------------------------
\section{Smoothing methods}
The smoothing methods considered in this article are now briefly explained.

@@

\begin{figure}
    \includegraphics[width=.99\linewidth]{z_img_hmtk_bsb2014_11_recurrence}
    \caption{Annual earthquake recurrence.}
    \label{fig_occurrence}
\end{figure}

>>>>

Figure \ref{fig_occurrence} presents the catalog \gls{mfd}. For the minimum magnitude the threshold was 2.9. The blue x and red crosses are the incremental and cumulative recurrence distributions binned by 0.2 magnitude unity. Stepp completeness table and \citet{bsb_2014} declustered catalogue was used. Also a fixed b-value (b=1) incremental distribution is shown in blue continuous line, and the fitted by maximum-likelihood method (magenta, $b=0.91\pm0.07$), \citet{weichert_1980} (green, $b=0.88\pm0.04$) and \citet{kijko_2012} (orange, $0.76\pm0.04$) are shown as continuous lines. The respective a-values was $3.7$, $3.8\pm0.2$, $3.5\pm0.2$, $3.2\pm0.1$. The minimum magnitude on that completeness table was 2.9.

COMMENT

@@

%------------------------------------------------
%
% smooothing methods
%
%------------------------------------------------
\section{Smoothing methods}
The smoothing methods considered in this article are now briefly explained and their results are discussed.

@@

\begin{figure}
    \includegraphics[width=.99\linewidth]{z_img_bsb2014_recurrence}
    \caption{Annual earthquake recurrence. The blue x and red crosses are the incremental and cumulative recurrence distributions binned by 0.2 magnitude unity. Stepp completeness table and \citet{bsb_2014} declustered catalogue was used. Also a fixed b-value (b=1) incremental distribution is shown in blue continuous line, and the fitted by maximum-likelihood method (magenta, $b=0.91\pm0.07$), \citet{weichert_1980} (green, $b=0.88\pm0.04$) and \citet{kijko_2012} (orange, $0.76\pm0.04$) are shown as continuous lines. The respective $10^a$ was $3.7$, $3.8\pm0.2$, $3.5\pm0.2$, $3.2\pm0.1$.
    }
    \label{fig_occurrence}
\end{figure}
